Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-11-17 Phase_II/draft/main.tex
block diagram
intro_reformatted, II.tex, refs.bib, Paragan.tex, main.tex changed
main.tex with DoI added

\documentclass[linenumbers, twocolumn]{aastex701}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows.meta, positioning, calc}

\tikzset{
	block/.style={
		rectangle,
		draw,
		rounded corners,
		minimum height=1cm,
		minimum width=3cm,
		align=center
	},
	arrow/.style={
		thick,
		-{Stealth}
	}
}

@@

>>>>

\documentclass[linenumbers, twocolumn]{aastex701}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
%\newcommand{\paperdoi}{10.5281/zenodo.17598807}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyfoot[L]{DOI: \href{https://doi.org/10.5281/zenodo.17598807}{10.5281/zenodo.17598807}}

\usetikzlibrary{shapes, arrows.meta, positioning, calc}

\tikzset{
	block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
	arrow/.style = {->, thick},
}

@@

%\maketitle
%\begin{center}
%\textbf{DOI:} \href{https://doi.org/\paperdoi}{\paperdoi}
%\end{center}
